---
title: "mtcars"
output: html_document
author: Y Sun
date: May 4, 2016
---

http://rmarkdown.rstudio.com/authoring_basics.html

#### Description

####Emphasis

*italic*   **bold**

_italic_   __bold__

####Headers

# Header 1

## Header 2

### Header 3

###Lists

#####Unordered List:
* Item 1
* Item 2
    + Item 2a
    + Item 2b

#####Ordered List:  
1. Item 1
2. Item 2
3. Item 3
    + Item 3a
    + Item 3b
    
####Miscellaneous
superscript^2^

~~strikethrough~~   

####Inline R Code
There were `r nrow(cars)` cars studied

####Links

http://example.com

[linked phrase](http://example.com)


#####Images


#####Blockquotes
A friend once said:

> It's always better to give
> than to receive.


#####Plain Code Blocks
```
This text is displayed verbatim / preformatted
```

####LaTeX Equations
####Inline equation:

$equation$

####Display equation:

$$ equation $$

####Horizontal Rule / Page Break

******

------


####Tables

First Header  | Second Header
------------- | -------------
Content Cell  | Content Cell
Content Cell  | Content Cell

####Links

A [linked phrase][id]

####At the bottom of the document:

[id]: http://example.com/ "Title"
Images
![alt text][id]


####Manual Line Breaks

Roses are red,
Violets are blue.


The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973–74 models).

```{r}
summary(cars)
```

You can also embed plots, for example:

```{r, echo=FALSE}
plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
